Title Goes Here

### 2024-04-18 analysis/paper/paper.qmd
uploaded carneige classification

# explore trends over time. put a point on the max year
jobdata_method_year_tally <-
  jobdata_method_year %>%
  # exclude those with <20 ads
  filter(!name %in% c("Digital Archaeology",
                      "Pleistocene archaeology",
                      "Mesoamerican Archaeology",
                      "Biological anthropology",
                      "Archaeological theory",
                      "Evolutionary anthropology",
                      "North American archaeology"
  )) %>%
  group_by(year_ad_posted,
           name) %>%
  summarise(n = sum(value)) %>%
  mutate(prop = n / sum(n))

@@

>>>>

# explore trends over time. put a point on the max year
jobdata_method_year_tally <-
  jobdata_method_year %>%
  # exclude those with <20 ads
  filter(!name %in% c("Material culture analysis"
  )) %>%
  group_by(year_ad_posted,
           name) %>%
  summarise(n = sum(value)) %>%
  mutate(prop = n / sum(n))

@@

```{r}
# Carneige Classification
library(googlesheets4)
library(stringi)

CC <-
  read_sheet( "https://docs.google.com/spreadsheets/d/1Oe_3X-OR7iuUThb6Tp48prBpbHrWjU4osmHKi1Hbqgc/edit#gid=1922578308",
             sheet = "Values1")
Basic2021 <-
  read_sheet( "https://docs.google.com/spreadsheets/d/1Oe_3X-OR7iuUThb6Tp48prBpbHrWjU4osmHKi1Hbqgc/edit#gid=1922578308",
             sheet = "Data1")

uni_name <- # 550
jobdata %>%  # 550 rows
 select(name_of_hiring_university) %>%
 mutate(name_of_hiring_university = str_replace(name_of_hiring_university, "\\s*\\(.*?\\)$", ""))

view(uni_name)
